\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-04 paper.tex
8. WOT Cleaning, extraneous stats.

In a three year study of over 30,000 MMORPG users, over 50\% of users said that they learned valuable leadership skills that have helped them outside of the game. \cite{MotivationsAndDerviedExperiences} To break it down further, 55.5\% of users believed they learned about conflict mediation, 48.4\% believed they learned about properly motivating a group, and 43.8\% believed they learned about persuading other members when a change in goals was necessary. \cite{MotivationsAndDerviedExperiences}
The study also showed that 45.8\% of users made friendships in the game that were comparable to or better than friendships they cultivated outside the game. 23.8\% of users had they most rewarding or satisfying experience in the game, as opposed to outside of the game, in the last 7 or 30 days. 28.6\% of users had their most annoying or infuriating experiences over the past 7 or 30 days occurring in the game. \cite{MotivationsAndDerviedExperiences}

Many features in World of Warcraft drive the players to socialize. \footnote{Having over two months of play time in-game with the last play session less than a week ago, I consider myself qualified to discuss the mechanics of World of Warcraft without citation.} The best gear and most prestigious titles are only available to users who group together to take on challenges that cannot be conquered by oneself. These challenges require intense coordination and communication as well as skilled players. Without grouping together, players have no chance of getting these items or attaining these statuses.
Guilds offer perks to their members through mechanics built into the game. As guilds grow in size and their members complete quests and dungeons, these guilds level up and offer rewards such as experience boosts allowing members to level faster, speed boosts allowing members to traverse the map faster, reputation gain boosts allowing members to increase their reputation with factions in the game that offer rewards, durability increases to its members' armor so that the armor does not need to be repaired nearly as often, increases in output from its members professions, and certain powerful spells that can be cast when guild members take on challenges together.

>>>>

In a three year study of over 30,000 MMORPG users, over 50\% of users said that they learned valuable leadership skills that have helped them outside of the game. \cite{MotivationsAndDerviedExperiences}
Many features in World of Warcraft drive the players to socialize. \footnote{Having over two months of play time in-game with the last play session less than a week ago, I consider myself qualified to discuss the mechanics of World of Warcraft without citation.} The best gear and most prestigious titles are only available to users who group together to take on challenges that cannot be conquered by oneself. These challenges require intense coordination and communication as well as skilled players. Without grouping together, players have no chance of getting these items or attaining these statuses.
Guilds offer perks to their members through mechanics built into the game. As guilds grow in size and their members complete quests and dungeons, these guilds level up and offer rewards such as experience boosts allowing members to level faster, speed boosts allowing members to traverse the map faster, reputation gain boosts allowing members to increase their reputation with factions in the game that offer rewards, durability increases to its members' armor so that the armor does not need to be repaired nearly as often, increases in output from its members professions, and certain powerful spells that can be cast when guild members take on challenges together.
